---
title: "COVID-19 Analysis for Indonesia"
author: "Victor T"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
```

## Data Loading

```{r data-loading}
# URLs for the datasets
confirmed_url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"
deaths_url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"
recovered_url <- "https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_recovered_global.csv"

# Reading the datasets
confirmed <- read_csv(confirmed_url)
deaths <- read_csv(deaths_url)
recovered <- read_csv(recovered_url)
```

## Data Preparation

```{r data-preparation}
# Function to transform data
prepare_data <- function(data, case_type) {
  data %>%
    filter(`Country/Region` == "Indonesia") %>%
    select(-`Province/State`, -Lat, -Long) %>%
    pivot_longer(cols = -`Country/Region`, names_to = "Date", values_to = case_type) %>%
    mutate(Date = mdy(Date))
}

# Preparing datasets
confirmed_long <- prepare_data(confirmed, "Confirmed")
deaths_long <- prepare_data(deaths, "Deaths")
recovered_long <- prepare_data(recovered, "Recovered")

# Merging datasets
covid_data <- confirmed_long %>%
  left_join(deaths_long, by = c("Country/Region", "Date")) %>%
  left_join(recovered_long, by = c("Country/Region", "Date")) %>%
  mutate(Active = Confirmed - Deaths - Recovered)
```

## Visualization 1: Time Series of Confirmed Cases

```{r time-series-plot}
covid_data %>%
  ggplot(aes(x = Date, y = Confirmed)) +
  geom_line(color = "blue") +
  labs(title = "Confirmed COVID-19 Cases in Indonesia",
       x = "Date",
       y = "Number of Cases") +
  theme_minimal()
```

## Visualization 2: Total Deaths, Recoveries, and Active Cases

```{r bar-plot}
# Latest data
latest_data <- covid_data %>%
  filter(Date == max(Date)) %>%
  select(Deaths, Recovered, Active) %>%
  pivot_longer(cols = everything(), names_to = "Case_Type", values_to = "Count")

# Bar plot
latest_data %>%
  ggplot(aes(x = Case_Type, y = Count, fill = Case_Type)) +
  geom_bar(stat = "identity") +
  labs(title = "COVID-19 Outcomes in Indonesia (Latest Data)",
       x = "Case Type",
       y = "Number of Cases") +
  theme_minimal()
```

## Analysis

As of the latest available data:

- **Total Confirmed Cases:** `r max(covid_data$Confirmed, na.rm = TRUE)`
- **Total Deaths:** `r max(covid_data$Deaths, na.rm = TRUE)`
- **Total Recovered:** `r max(covid_data$Recovered, na.rm = TRUE)`
- **Total Active Cases:** `r max(covid_data$Active, na.rm = TRUE)`

The time series plot illustrates the progression of confirmed COVID-19 cases in Indonesia over time, showing significant increases during certain periods. The bar plot provides a snapshot of the current distribution of outcomes, highlighting the proportions of deaths, recoveries, and active cases.
